Paper 1

### 2022-08-01 scripts/Paper 1.Rmd
remove commit figs to this

(rainfall.p <-rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
  ddply(c("monthyear", "Year"), summarise,
  monthly.total = sum(Precip)) %>%
  ggplot(., aes(x = monthyear, y = monthly.total)) +
  geom_col(position = "dodge") +
  scale_x_yearmon(n = 7, expand = c(0,0))+
  ylab("Monthly rainfall (mm)")+
  xlab("Date")+
  theme_classic()+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14),
          axis.text.x = element_text( vjust = 0.5)))
rainfall.p
tiff("rainfall.tiff", units="in", width=10, height=6,  res=300)
print(rainfall.p)
dev.off()

@@

TA
tiff("TA.tiff", units="in", width=10, height=6,  res=300)
print(TA)
dev.off()

TS
tiff("TS.tiff", units="in", width=10, height=6,  res=300)
print(TS)
dev.off()
```

@@

TA.sum.p
tiff("TAbar.tiff", units="in", width=10, height=6,  res=300)
print(TA.sum.p)
dev.off()

@@

TS.sum.p
tiff("TSbar.tiff", units="in", width=10, height=6,  res=300)
print(TS.sum.p)
dev.off()

@@

(ET.p <- ggplot(input.rearranged, aes(x = dayssinceJun1, y = ET, group = GSYear)) +
  geom_line(aes(color = GSYear), size = 1)+
    scale_color_manual(values = group.colour) +
 # scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  xlab("Days since June 1st")+
   ylab("ET (mm day-1)")+
  theme_classic())+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14))

@@

#  ylab('SWC') +
  # scale_x_continuous()+
    scale_color_manual(values=group.colour)+
  theme_classic() + 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.position = "none"))

@@

NEE.bar
tiff("NEEbar.tiff", units="in", width=10, height=6,  res=300)
print(NEE.bar)
dev.off()
```

@@

GPP.bar
tiff("GPPbar.tiff", units="in", width=10, height=6,  res=300)
print(GPP.bar)
dev.off()
```

@@

ER.bar
tiff("ERbar.tiff", units="in", width=10, height=6,  res=300)
print(ER.bar)
dev.off()
```

@@

NEEcum.p
tiff("NEEcum.tiff", units="in", width=10, height=6,  res=300)
print(NEEcum.p)
dev.off()

@@

GPPcum.p
tiff("GPPcum.tiff", units="in", width=10, height=6,  res=300)
print(GPPcum.p)
dev.off()

@@

GPPtime.p
tiff("GPPtime.tiff", units="in", width=10, height=6,  res=300)
print(GPPtime.p)
dev.off()

@@

ERcum.p
tiff("ERcum.tiff", units="in", width=10, height=6,  res=300)
print(ERcum.p)
dev.off()

@@

ERtime.p
tiff("ERtime.tiff", units="in", width=10, height=6,  res=300)
print(ERtime.p)
dev.off()

@@

Fig2
tiff("Fig2.tiff", units="in", width=10, height=6,  res=300)
print(Fig2)
dev.off()

@@

GPP.bar.s
tiff("GPPbar.tiff", units="in", width=10, height=6,  res=300)
print(GPP.bar.s)
dev.off()

@@

ER.bar.s
tiff("ERbar.tiff", units="in", width=10, height=6,  res=300)
print(ER.bar.s)
dev.off()

>>>>

(rainfall.p <-rainfall %>%  mutate(Precip = replace_na(Precip, 0)) %>%
  ddply(c("monthyear", "Year"), summarise,
  monthly.total = sum(Precip)) %>%
  ggplot(., aes(x = monthyear, y = monthly.total)) +
  geom_col(position = "dodge") +
  scale_x_yearmon(n = 7, expand = c(0,0))+
  ylab("Monthly rainfall (mm)")+
  xlab("Date")+
  theme_classic()+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14),
          axis.text.x = element_text( vjust = 0.5)))
rainfall.p
#tiff("rainfall.tiff", units="in", width=10, height=6,  res=300)
#print(rainfall.p)
#dev.off()

@@

TA
#tiff("TA.tiff", units="in", width=10, height=6,  res=300)
#print(TA)
#dev.off()

TS
#tiff("TS.tiff", units="in", width=10, height=6,  res=300)
#print(TS)
#dev.off()
```

@@

TA.sum.p
#tiff("TAbar.tiff", units="in", width=10, height=6,  res=300)
#print(TA.sum.p)
#dev.off()

@@

TS.sum.p
#tiff("TSbar.tiff", units="in", width=10, height=6,  res=300)
#print(TS.sum.p)
#dev.off()

@@

(ET.p <- ggplot(input.rearranged, aes(x = dayssinceJun1, y = ET, group = GSYear)) +
  geom_line(aes(color = GSYear), size = 1)+
    #scale_color_manual(values = group.colour) +
 # scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  xlab("Days since June 1st")+
   ylab("ET (mm day-1)")+
  theme_classic())+
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14))

@@

#  ylab('SWC') +
  # scale_x_continuous()+
    #scale_color_manual(values=group.colour)+
  theme_classic() + 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.position = "none"))

@@

NEE.bar
#tiff("NEEbar.tiff", units="in", width=10, height=6,  res=300)
#print(NEE.bar)
#dev.off()
```

@@

GPP.bar
#tiff("GPPbar.tiff", units="in", width=10, height=6,  res=300)
#print(GPP.bar)
#dev.off()
```

@@

ER.bar
#tiff("ERbar.tiff", units="in", width=10, height=6,  res=300)
#print(ER.bar)
#dev.off()
```

@@

NEEcum.p
#tiff("NEEcum.tiff", units="in", width=10, height=6,  res=300)
#print(NEEcum.p)
#dev.off()

@@

GPPcum.p
#tiff("GPPcum.tiff", units="in", width=10, height=6,  res=300)
#print(GPPcum.p)
#dev.off()

@@

GPPtime.p
#tiff("GPPtime.tiff", units="in", width=10, height=6,  res=300)
#print(GPPtime.p)
#dev.off()

@@

ERcum.p
#tiff("ERcum.tiff", units="in", width=10, height=6,  res=300)
#print(ERcum.p)
#dev.off()

@@

ERtime.p
#tiff("ERtime.tiff", units="in", width=10, height=6,  res=300)
#print(ERtime.p)
#dev.off()

@@

Fig2
#tiff("Fig2.tiff", units="in", width=10, height=6,  res=300)
#print(Fig2)
#dev.off()

@@

GPP.bar.s
#tiff("GPPbar.tiff", units="in", width=10, height=6,  res=300)
#print(GPP.bar.s)
#dev.off()

@@

ER.bar.s
#tiff("ERbar.tiff", units="in", width=10, height=6,  res=300)
#print(ER.bar.s)
#dev.off()
